---
title: "TADA: Lobbying Influence on Congressmembers' Tweets"
author: "Jean Pierre Salendres, Sarah Kennedy, and Michelangelo Freyrie "
date: "12/21/2020"
output:
  html_document:
    theme: lumen
    highlight: espresso
    toc: yes 
    toc_depth: 2 
    toc_float: true 
    number_sections: true
---

<style type="text/css">

body{ /* Normal  */
      font-size: 12px;
  }
td {  /* Table  */
  font-size: 8px;
}
h1.title {
  font-size: 38px;
  color: cornflowerblue;
}
h1 { /* Header 1 */
  font-size: 24px;
  color: cornflowerblue;
}
h2 { /* Header 2 */
    font-size: 22px;
  color: DarkBlue;
}
h3 { /* Header 3 */
  font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: DarkBlue;
}
code.r{ /* Code block */
    font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 14px;
}
</style>

<style>
.nav>li>a {
    position: relative;
    display: block;
    padding: 10px 15px;
    color: cornflowerblue;
}
.nav-pills>li.active>a, .nav-pills>li.active>a:hover, .nav-pills>li.active>a:focus {
    color: #ffffff;
    background-color: cornflowerblue;
}
</style>

<style type="text/css">
#TOC {
  color: cornflowerblue;
}

</style>
<style type="text/css">

body, td {
   font-size: 16px;
}
</style>

# Idea and Research Question  {.tabset .tabset-fade .tabset-pills} 

We set out to understand the impact of lobbying on Congressional communication on Twitter. 

What can lobbying funds tell us about Congress members public rhetoric about key issues?

We will look specifically at two fields: the environment and gun control. 

*Hypothesis*: We expect that Congresspeople who receive more funds from lobbyists on bills they have sponsored related to gun control or the environemnt will tweet more often about these respective issues. Moreover, controlling for party, higher lobbying levels will also lead to more negatively/positively charged speech on these issues. 

We chose to work with data from the House of Representatives because they are typically more closely aligned with local interests and are more accountable to them (as they represent a smaller group of citizens) than Senators. 

# DATA  {.tabset .tabset-fade .tabset-pills} 

## LOBBYING {.tabset .tabset-fade .tabset-pills} 

### *Lobby Data Acquisition*:
Using data acquired from LobbyView.org, a group dedicated to “advancing data science research in interest group politics,” we were able to determine the amount of money received by congresspeople in 2019 and 2020 per bill that they sponsored. All examined bills were related to gun issues.  
To explore the influence of lobbying contributions on Twitter speech, we needed lobby monetary contribution data for 1) environment and gun legislation and for 2) individual members of Congress. 
LobbyView is an open-source website with lobby data for the United States. Their data spans the entire government. We focused on lobbying made to members of the House of Representatives (to match our Twitter data). The original data is sprad over 5 spreadsheets and we focused on gathering the relevant area and segmenting it in order to downsize files and have the specific data necessary for our study. 
<br>

The Lobby data is linked to bills sponsored in the House of Representatives and we link this money to Congressmen sponsors of the bill. This means that the monetary lobby contriution is not direct to the congress member but encompasses a lobby effort for the sponsored bill in question.
This link is sufficient since our hypothesis points to these lobbying contributions as influencers of debate on the house floor (sponsored bills) and Congress member's public rhetoric (Tweets). 

Our large lobby dataset contains dozens of variables that help us match data to twitter handles, Congressmen names, lobby firms, house bills, dates, etc.
For simplicity of our treatment study (effect of lobbying), we segmented this data into two sub-datasets. 
Both our 'gun' (df_money_gun_peryear) and 'environment' (df_money_env_peryear) lobbying sub-datasets contain the folowing variables:

- `report_year`: year of lobby contributions
- `congressman_twitter_handle`: Congressman handle for lobby recipient 
- `amount`(**treatment variable**): the percentage of voters from the total number of eligible registered voters for a given county
- `issue_code`: the presence of centralized vote center
<br>

### LOBBYING VISUALIZATION

From the two graphs below, we can see the variation of lobby contributions for sponsors of gun-related bills and sponsors of environemntal-related bills. The gun-related lobbying  for individual Congress members goes up to 25,000 dollars per year, while the environmental-related lobbying for individual Caongress members goes past a million dollars.

It is important to note thet in the environemntal-related lobbying chart below we have included various lobby areas that are linked in some way to the general idea of environment. We expect that most of these areas will have a negative speech effect, or abstinence of pro-environemnt speech, on Congressmen i.e. Chemicals, Fuels, Transport). Environment is the only variable that we expect to have a positive effect on speech pro-environment. Lastly, we expect Energy to be mixed and produce more conversation on the environment but on both negative and positive directions, due to the variance of energy groups across energy sources (some more environmentally-friendly than others).


```{r, warning=FALSE}
env_lobby_graph
```

```{r, warning=FALSE}
gun_lobby_graph
```

## TWEETS {.tabset .tabset-fade .tabset-pills} 

### *Twitter Data Acquisition*:
Using the Twitter API, we pulled 75,000 (25k/group member) Tweets from all 435 Members of the House of Representatives’ official accounts. We took a list of Congressmen from the 115th Congress (Jan 2017- Jan 2019). The tweets span from 205 to 2020, as some Congressmen have been in Congress pre-115th Congress and post 115th Congress. We keep these dates in mind throughout the analysis and focus on the 115th Congress (full list of members) but consider pre and post 115th congress data to see Congress members longer speech trends. 


We use this data as evidence of the political communication surrounding important issues for the Congress member and his audience, including on gun control and environmental legislation. We assume that there is an incentive for congress members to use Twitter communication to disseminated their views and political interests. 

Below are a few visualizations of the twitter data we have for all Congress members:

Here we see the frquency of words most used in tweets. The terms are quite general and political in nature (america, support, pass, vote, legislation, great, trump, right, care). But these are too broad for our interests.
```{r, warning=FALSE}
twitter_plot2
```

Zooming in to conversation about guns, we see the lexical dispersion for the word "guns" and how it varies in use by congressmen. 
```{r, warning=FALSE}
dispersion_plot
```

Below we can see from our gun-dictionary, the results when applied to our twitter data. 
```{r, warning=FALSE}
dictionary_plot
```
 

# ANALYSIS

Representatives were grouped into three levels (low/medium/high) by how much total money they received from interest groups for all of the examined bills.
We examined the collocations of the word “gun” and created a dictionary that incorporated those phrases. The amount of documents per user name was 


We looked at the amount of tweets using the keywords for gun and enviornmental legislation, under the assumption that Republicans are not supportive of (and therefore discuss less) firearm regulation or climate policy and Democrats are. 
From this we compared the Representative’s level of funding from interest groups (on sponsored bills) to their tweets average negative-positive sentiment regarding firearms legislation. 

# FINDINGS  

XXX

# Code {.tabset .tabset-fade .tabset-pills} 
## TADA Project Code {.tabset .tabset-fade .tabset-pills} 
### Matching Tweets to Political Party
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

```{r, include = FALSE}

library(quanteda)
library(glmnet)
library(quanteda)
library(readtext)
library(corpus)
library(tibble)
library(readr)
library(dplyr)
library(xtable)
library(stm)
library(rtweet)
library(tidyverse)
library(rvest)
library(pdftools)
library(stringr)
library(tm)
library(textreadr)
library(bpa)

```

```{r}

consolidated_congress_data <- read_delim("consolidated congress data.csv", 
    ";", escape_double = FALSE, col_names = FALSE, 
    trim_ws = TRUE)

data <- read_csv("tmls.csv")

data1 <- mutate(data, date = as.POSIXct(as.numeric(data$created_at), origin = '1970-01-01', tz = 'GMT')) %>% subset(select = -c(status_id, urls_url, reply_count, created_at, quote_count)) %>% subset(date > '2015-01-01')

party <- select(consolidated_congress_data,X1, X3, X10, X11) 
colnames(party)  <- c("chamber","Party","Lobby_code","handle")

screen_name <- tolower(party$handle) 
party <- cbind(party, screen_name)%>%
  na.omit()%>%
  select(-handle)

data1 <- merge(party, data1, by = "screen_name") 
```

### Creating Corpus

```{r}

#Since we only have one relevant text column:
my_corp <- corpus(data1, 
                  docid_field = 'X1', text_field = 'text')

#example of 100 characters of first text
txts <- texts(my_corp)
substr(txts[1], 1, 100)

#how does our corpus look like
summary(my_corp, n = 10)

#Key terms in play

tokens <- tokens(
  my_corp,
  what = "fasterword",
  remove_punct = TRUE,
  remove_symbols = TRUE,
  remove_numbers = FALSE,
  remove_url = TRUE,
  remove_separators = TRUE,
  split_hyphens = TRUE)

```

### Collocations
```{r}
# collocation 
colls <- textstat_collocations(tokens)
head(colls, 20)

#three word collocations, do we see trends?
#coll3 <- textstat_collocations(tokens, tolower = FALSE, size = 3)
#head(coll3, 30)

#how is gun talked about
gun1 <- kwic(my_corp, "gun*", window = 10)
head(gun1, 20)

#how is environment talked about
env1 <- kwic(my_corp, "environment*", window = 10)
View(env1)

env2 <- kwic(my_corp, "climate*", window = 8)
View(env2)

#env3 <- kwic(my_corp, "natural", window =8)
#View(env3)

#if we want to look at a phrase used in corpus
phrase1 <- kwic(tokens, phrase("gun violence"))

phrase2 <- kwic(tokens, phrase("climate change"))

#or if we want to look at all phrases that come up in our colloc
#phrases <- phrase("XXXX", "YYYY")
#toks <- tokens_compound(tokens, phrases)
```


```{r}
#Applied to each of our areas of interest
# First Gun speech

guns <- kwic(my_corp, "gun*", window = 10)

guns_df <- tibble(screename = guns$docname, 
                   text = paste(guns$pre, guns$post, sep = " "))
corp_guns <- corpus(guns_df)
summary(corp_guns)

#Second for environment speech

env <- kwic(my_corp, "environment*", window = 10)

env_df <- tibble(screename = env$docname, 
                   text = paste(env$pre, env$post, sep = " "))
corp_env <- corpus(env_df)
summary(corp_env)

#we can look at collocations by gun or env segment:
#guns_wording <- textstat_collocations(corp_guns, size = 2)
#env_wording <- textstat_collocations(corp_env, size = 4)

#on to a dfm
dfm <- dfm(my_corp, remove = stopwords("english"), 
           stem = TRUE, remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE, split_hyphens = TRUE)
featnames(dfm)[1:40]
head(dfm)

#subset to get rid of retweets
dfm_new <- dfm_subset(dfm, is_retweet == FALSE)

#use of words by party
corpdfm_party <- dfm(dfm_new, groups = "Party")
small_corpdfm_party <- dfm_trim(corpdfm_party, min_docfreq = 2) #min 2 times word appears across all docs, cuts data

#frequencies
dfm_party <- dfm_group(corpdfm_party, "Party")

rep_terms <- textstat_keyness(dfm_party, "Republican")
head(rep_terms, 25)
dem_terms <-  textstat_keyness(dfm_party, "Democrat")
head(dem_terms, 25)

#stats on our groups
ntoken(dfm_party) # words on each side
```

### Dictionaries
Creating dictionary for Guns
```{r}

#Dictionary using collocations list

guns_dic1 <- dictionary(list(guns = c('gun*violence', 'gun*safety', 'sense', 'prevent','commonsense*gun', 'senseless*gun', 'gun*lobby', 'gun*storage', 'gunviolence*prevention', 'unsecured*gun', 'gun*')))
                                     
#check party dfm against new dictionary
dfm_party_dic <- dfm(dfm_new, dictionary = guns_dic1, group = "Party")
View(dfm_party_dic)

individ_guns <- dfm(dfm_new, dictionary = guns_dic1, group = "screen_name")
View(individ_guns)
```

Climate Change Dictionary Bit

```{r}
envi_dic <- dictionary(list(envi = c('climate*','environmental*protection', 'environmental*resources', 'the*arctic', 'natural*resources', 'interior', 'EPA', 'climate*', 'natural*disaster', 'natural*gas')))
                                     
#check party dfm against new dictionary
dfm_envi_dic <- dfm(dfm, dictionary = envi_dic, group = "Party")

View(dfm_envi_dic)

dfm_individ <- dfm(dfm, group = "screen_name", dictionary = envi_dic)

View(dfm_individ)
```

```{r}
full_dic <- dictionary(list(envi = c('climate','environmental protection', 'environmental resources', 'arctic', 'natural resources', 'interior', 'EPA', 'climate*', 'natural disaster', 'natural gas'), guns = c("gun violence", "gun safety",'sense', 'prevent','commonsense gun', 'senseless gun', 'gun lobby', 'gun storage', 'gunviolence prevention', 'unsecured gun', 'gun*'))) 

subdfm_full <- dfm(dfm_party) %>%
    dfm_select(pattern = full_dic, valuetype = "glob")

features_dfm_full <- textstat_frequency(subdfm_full, n = 40)

# Sort by reverse frequency order
features_dfm_full$feature <- with(features_dfm_full, reorder(feature, -frequency))

#plot
dictionary_plot <- ggplot(features_dfm_full, aes(x = feature, y = frequency)) +
    geom_point() + 
    theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  theme_bw()

dictionary_plot
```


```{r}
my_corp2 <- my_corp
docnames(my_corp2) <- apply(docvars(my_corp2, c("screen_name", "Party")), 1, paste, collapse = ", ")
summary(my_corp2, n = 10)

dispersion_plot <- kwic(my_corp2, pattern = "guns") %>%
    textplot_xray()

```

## Lobby Data Code

```{r}
#downsize sponsored bills
sponsored_bills <- read_delim("sponsored_bills.csv",";", escape_double = FALSE, trim_ws = TRUE)
new1 <- subset.data.frame(sponsored_bills, sponsored_bills$report_year > "2014")
new_sponsored_bills <- na.omit(new1, Var = c("congress_id_handles.Tweetcongress"))
write.csv(new_sponsored_bills,"new_sponsored_bills", row.names = FALSE)

#downsize lobbying contributions file
dataset_report_level <- read_csv("dataset___report_level.csv")
money1 <- subset.data.frame(dataset_report_level, dataset_report_level$report_year > "2014") 
money2 <- subset.data.frame(money1, money1$amount != "$0.00")
write.csv(money2,"new_dataset_report_level", row.names = FALSE)

#merge amount with congressmen dataset 
TADA_data <- merge(x = money2, y = new_sponsored_bills, by = "client_uuid", all = FALSE)
write.csv(TADA_data,"TADA_data", row.names = FALSE)

#downsize issue code lobby data to relevant ones for and environment
dataset_issue_level <- read_csv("dataset___issue_level.csv")
issues_env1 <- subset.data.frame(dataset_issue_level, dataset_issue_level$issue_code == list("ENV", "TRA","FUE","ENG", "NAT", "CHM")) 
issues_env <- subset.data.frame(issues_env1, issues_env1$gov_entity == '{"HOUSE OF REPRESENTATIVES",SENATE}')

#downsize issue code lobby data to relevant ones for and environment
issues_gun1 <- subset.data.frame(dataset_issue_level, dataset_issue_level$issue_code == "FIR") 
issues_gun <- subset.data.frame(issues_gun1, issues_gun1$gov_entity == '{"HOUSE OF REPRESENTATIVES",SENATE}')

#DATA ENV : merge with issue codes, this will be the FINAL dataset on the lobby side we will need. 
TADA_env_data <- merge(x = TADA_data, y = issues_env, by = "report_uuid", all = FALSE)
write.csv(TADA_env_data,"TADA_env_2015-2020", row.names = FALSE)

#DATA GUN : merge with issue codes, this will be the FINAL dataset on the lobby side we will need. 
TADA_gun_data <- merge(x = TADA_data, y = issues_gun, by = "report_uuid", all = FALSE)
write.csv(TADA_gun_data,"TADA_gun_2015-2020", row.names = FALSE)

#add up total lobby for each congressmen dataset
TADA_gun_data$amount <- as.factor(as.character(TADA_gun_data$amount)) 
TADA_gun_data$amount <- as.numeric(as.factor(TADA_gun_data$amount)) 
sapply(TADA_gun_data, class)


TADA_env_data$amount <- as.factor(as.character(TADA_env_data$amount)) 
TADA_env_data$amount <- as.numeric(as.factor(TADA_env_data$amount)) 
sapply(TADA_env_data, class)

#sum for each congressman lobby money for env
money_env_totals <- TADA_env_data %>%
  group_by(congress_id_handles.TweetCongress, issue_code) %>% 
  transmute(Total=sum(amount))

money_env_peryear <- TADA_env_data %>%
  group_by(congress_id_handles.TweetCongress, issue_code, report_year.x) %>% 
  transmute(Total=sum(amount))

#sum for each congressman lobby money for guns
money_gun_totals <- TADA_gun_data %>%
  group_by(congress_id_handles.TweetCongress, issue_code) %>% 
  transmute(Total=sum(amount))

money_gun_peryear <- TADA_gun_data %>%
  group_by(congress_id_handles.TweetCongress, issue_code, report_year.x) %>% 
  transmute(Total=sum(amount))

#unique senators with contributions to their name
df_money_env <- unique(money_env_totals)
write.csv(df_money_env,"df_money_env", row.names = FALSE)

df_money_env_peryear <- unique(money_env_peryear)
write.csv(df_money_env_peryear,"df_money_env_peryear", row.names = FALSE)

df_money_gun <- unique(money_gun_totals)
write.csv(df_money_gun,"df_money_gun", row.names = FALSE)

df_money_gun_peryear <- unique(money_gun_peryear)
write.csv(df_money_gun_peryear,"df_money_gun_peryear", row.names = FALSE)
```

```{r}
#plotting the data 
options(scipen=999)

env_lobby_graph <- ggplot(df_money_env_peryear) +
  aes(x = report_year.x, y = Total, color = issue_code, fill=issue_code) +
  geom_text(aes(label = congress_id_handles.TweetCongress), check_overlap = TRUE,
  size = 1.8,
  vjust = -1) +
  scale_x_continuous(name="Lobbying Years", limits=c(2015, 2020)) +
  scale_y_continuous(name="Environment Lobbying Amount", limits=c(30000, 100000)) +
  scale_color_discrete(name = "Lobby Areas", labels = c("Chemicals", "Energy","Environment","Fuels", "Natural Resources", "Transport"))



gun_lobby_graph <- ggplot(df_money_gun_peryear) +
  aes(x = report_year.x, y = Total) +
  geom_text(aes(label = congress_id_handles.TweetCongress), check_overlap = TRUE,
  size = 1.8,
  vjust = -1) +
  scale_x_continuous(name="Lobbying Years", limits=c(2015, 2020)) +
  scale_y_continuous(name="Gun Lobbying Amount", limits=c(0, 25000)) 
  

```

## Tweet API Code
```{r, eval=F, echo=T}

api_key1 <- "8iJelpReXMwWR5xUSY6TzrESY"
api_secret_key1 <- "LRZVxZ3ew0CyP6ixogTfvxr40nOIU0yUfMa1crieTlvvsOmkSD"

token1 <- create_token(
  app = "pesco-app",
  consumer_key = api_key1,
  consumer_secret = api_secret_key1)

handles_top <- head(handles2, n=176)

tmls <- get_timelines(
  handles_top$User, n = 25000)

write.table(tmls, file = "tmls_01-176.csv")
write.csv()
```

```{r}

#Create Frequency Plot 
no_U <- dfm_remove(dfm_party, pattern = c("@*", "U", "#*", "amp", "today", "s*", "", "t", "w", "can", "fe0f"))
no_U2 <- dfm_remove(no_U, stopwords("en"))

features_dfm_tweets <- textstat_frequency(no_U2, n = 60)

# Sort by reverse frequency order
features_dfm_tweets$feature <- with(features_dfm_tweets, reorder(feature, -frequency))

twitter_plot2 <- ggplot(features_dfm_tweets, aes(x = feature, y = frequency)) +
    geom_point() + 
    theme(axis.text.x = element_text(angle = 90, hjust = 1))


```

```{r}
library(rtweet)
library(igraph)
library(hrbrthemes)
library(ggraph)
library(tidyverse)

tmls <- read_csv("tmls.csv")

filter(tmls, retweet_count > 0) %>% 
  select(screen_name, mentions_screen_name) %>%
  unnest(mentions_screen_name) %>% 
  filter(!is.na(mentions_screen_name)) %>% 
  graph_from_data_frame() -> rt_g

V(rt_g)$node_label <- unname(ifelse(degree(rt_g)[V(rt_g)] > 20, names(V(rt_g)), "")) 
V(rt_g)$node_size <- unname(ifelse(degree(rt_g)[V(rt_g)] > 20, degree(rt_g), 0)) 

twitter_plot <- ggraph(rt_g, layout = 'linear', circular = TRUE) + 
  geom_edge_arc(edge_width=0.125, aes(alpha=..index..)) +
  geom_node_label(aes(label=node_label, size=node_size),
                  label.size=0, fill="#ffffff66", segment.colour="springgreen",
                  color="slateblue", repel=TRUE, fontface="bold") +
  coord_fixed() +
  scale_size_area(trans="sqrt") +
  labs(title="Retweet Relationships", subtitle="Most retweeted screen names labeled. Darkers edges == more retweets. Node size == larger degree")

twitter_plot
```

```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE, results = "asis"}

#data frame matrix from applying gun dictionary and convert to data frame

individ_guns_final <- as.data.frame(
  individ_guns,
  row.names = NULL,
  document = docnames(individ_guns),
  docid_field = "congress_id_handles.TweetCongress",
  check.names = FALSE
)

#data frame matrix from applying env dictionary and comvert to data frame

individ_env_final <- as.data.frame(
  dfm_individ,
  row.names = NULL,
  document = docnames(dfm_individ),
  docid_field = "congress_id_handles.TweetCongress",
  check.names = FALSE
)


#Calculating basic regression model to test correlation of our hypothesis 
#GUN
reg_basic <- lm(twitter ~ amount + issue_code, df_money_gun_peryear)
stargazer(reg_basic, type ="html")

#ENVIRONMENT
reg_basic2 <- lm(twitter ~ amount + issue_code, df_money_env_peryear)
stargazer(reg_basic2, type ="html")

```
